\LARGE \bf Geometric Adaptive Control of Attitude Dynamics on $\SO$\\ with State Inequality Constraints

### 2015-09-20 ACC16.2.tex
removed unneeded files and changed name to follow dr. lee's format

\title{\LARGE \bf
Constrained Attitude Control
}

@@

\section{Attitude Control on $\SO$ with Inequality Constraints}
Constructing configuration error function

@@

Show stabilization with and without repulsive term
Show stabilization with and without adaptive update law

@@

Get the configuration error function mapped onto the attitude sphere

>>>>

@@

\section{Attitude Control on $\SO$ with Inequality Constraints}
Discuss importance of choosing a configuration error function

Constructing configuration error function

Log barrier for repulsive term

Standard attractive error function

cite bullo and Dr. Lee papers

@@

Inertia matrix of hexrotor

control gains

define sensor and constraint axis

Define initial and desired condition

Present three cases

Show stabilization without repulsive term (passes through constraint)
Show stabilization with avoidance term without disturbance
Show stabilization with disturbance and adaptive update law

@@
